Growing libraries of concepts with wake-sleep program induction

### 2018-07-24 talk.tex
improvements to final slide
even more tweaks to the final slide

  \begin{itemize}
  \item Library of concepts (declarative knowledge)
    \item Search strategy (procedural knowledge)
    \end{itemize}
\end{frame}

@@

   \underline{More human-like machine intelligence}\\Flexibly adapting to new problem domains:
   acquiring a domain-specific language-of-thought (DSL); learning how to use the language of thought (recognition model)

@@

\hspace{-1cm}\includegraphics[width = 12cm]{figures/finale.png} 
  \end{frame}

>>>>

  \begin{itemize}
  \item Library of concepts (declarative knowledge)
    \item Inference strategy (procedural knowledge)
    \end{itemize}
\end{frame}

@@

   \underline{More human-like machine intelligence}\\%Flexibly adapting to new problem domains:
   \begin{itemize}
   \item    Acquiring a domain-specific language-of-thought (DSL)
     \item Learning  to use the language of thought (recognition model)
   \end{itemize}
   DreamCoder: an algorithm for jointly realizing these goals

   \hspace{-1cm}\includegraphics[width = 12cm]{figures/finale.png}

@@

   \Huge \centering \textbf{The End.}
  \end{frame}
